taxadb: A High-Performance Local Taxonomic Database Interface

### 2020-01-21 paper/manuscript.Rmd
Add in table references.

These issues are best illustrated using a minimal example.  We'll consider the task of combining data on bird extinction risk as assessed by the IUCN [@iucn] with data on average adult biomass, as estimated in the Elton Traits v1.0 database [@elton-traits.]  To keep the example concise enough for for visual presentation we will focus on a subset involving just 10 species [\@ref(tab:iucn_table)]

@@

If we attempted to join these data directly on the species names provided by each table, we would find very little overlap, with only one species having both a body mass and an IUCN threat status resolved:

@@

This results in many more matches, as different scientific names are recognized by the naming provider (Catalog of Life 2018 in this case), as *synonyms* for the same species, and thus resolve to the same taxonomic identifier.  While we have focused on a small example for visual clarity here, the `get_ids()` function in `taxadb` can quickly resolve hundreds of thousands of species names to unique identifiers, thanks to the performance of fast joins in a local MonetDBLite database.

@@

We see that *Zosterops rendovae* matches two accepted names which the user will have to choose between.

@@

### Supported providers

>>>>

These issues are best illustrated using a minimal example.  We'll consider the task of combining data on bird extinction risk as assessed by the IUCN [@iucn] with data on average adult biomass, as estimated in the Elton Traits v1.0 database [@elton-traits.]  To keep the example concise enough for for visual presentation we will focus on a subset involving just 10 species (Table 1, 2).

@@

If we attempted to join these data directly on the species names provided by each table, we would find very little overlap, with only one species having both a body mass and an IUCN threat status resolved (Table 3).

@@

This results in many more matches (Table 4), as different scientific names are recognized by the naming provider (Catalog of Life 2018 in this case), as *synonyms* for the same species, and thus resolve to the same taxonomic identifier.  While we have focused on a small example for visual clarity here, the `get_ids()` function in `taxadb` can quickly resolve hundreds of thousands of species names to unique identifiers, thanks to the performance of fast joins in a local MonetDBLite database.

@@

We see that *Zosterops rendovae* matches two accepted names which the user will have to choose between (Table 5).

@@
